05_DESeq_manipulation

### 2019-05-16 analysis/05_DESeq2_manipulate.Rmd
now with 500

sigDEGs <- DEGs %>% arrange(padjmin)
sigDEGs <- head(sigDEGs,300)
sigDEGs <- as.data.frame(sigDEGs)
rownames(sigDEGs) <- sigDEGs$rownames
drop.cols <-colnames(sigDEGs[,grep("padj|pval|pmin|rownames", colnames(sigDEGs))])
sigDEGs <- sigDEGs %>% dplyr::select(-one_of(drop.cols))
sigDEGs <- as.matrix(sigDEGs)
sigDEGs <- sigDEGs - rowMeans(sigDEGs)

>>>>

sigDEGs <- DEGs %>% arrange(padjmin)
sigDEGs <- head(sigDEGs,500)
sigDEGs <- as.data.frame(sigDEGs)
rownames(sigDEGs) <- sigDEGs$rownames
drop.cols <-colnames(sigDEGs[,grep("padj|pval|pmin|rownames", colnames(sigDEGs))])
sigDEGs <- sigDEGs %>% dplyr::select(-one_of(drop.cols))
sigDEGs <- as.matrix(sigDEGs)
sigDEGs <- sigDEGs - rowMeans(sigDEGs)
